\chapter{Question 1}
\label{intro}

\textbf{Choose a blog or a newsfeed (or something similar with an Atom or RSS feed).  Every student should do a unique feed, so please
``claim'' the feed on the class email list (first come, first served). It should be on a topic or topics of which you are qualified to provide classification training data.  Find something with at least 100 entries (or items if RSS).\\\\
Create between four and eight different categories for the entries in the feed:\\\\
examples: \\\\
work, class, family, news, deals\\\\
liberal, conservative, moderate, libertarian\\\\
sports, local, financial, national, international, entertainment\\\\
metal, electronic, ambient, folk, hip-hop, pop\\\\
Download and process the pages of the feed as per the week 12  class slides.\\\\
Be sure to upload the raw data (Atom or RSS) to your github account.}\\\\

\newpage
Following are the steps I have taken to the solve the problem:
\begin{itemize}
\item The most hardest part in the assignment is to find the blog with atleast 100 entries. I tried searching different blogs of my favorite cricketer, actor, restaurants etc. But I could find a blog. I tried even paginating the blogs but they did not have more than 100 Entries.
\item Finally I started searching newsfeed and I found an entertainment feed in `Times of India'.
\item It has about 172 items. I worked on 86 items manually and the remaining using the fisher classification.
\item Based on their language, I categorized the items in the feed into 12 categories. The categories are as follows: `Hindi', `Telugu', `English', `Malayalam', `Kannada', `Marathi', `Gujarathi', `Punjabi', `Bhojpuri', `Tamil', `Bengali' and `others'. 
\end{itemize}
